### 2022-02-22 draft2.tex
revisions to representations section

\usepackage{framed}
\usepackage{changepage}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

@@

A probabilistic forecast is a probability distribution that may be represented
in a few different formats. A common representation is either a continuous or
discrete parametric distribution function (a pdf or pmf). Much of the literature 
on calibration, sharpness and scoring of a forecast pertains to parametric 
distribution forecasts (see for example 
\cite{gneiting2007probabilistic},
\cite{gneiting2013combining} \cite{baran2018combining}).
Other common representations include samples \cite{krueger2016probabilistic}, 
discretized bins 
and quantile or interval type forecasts \cite{taylor2021evaluating} 
\cite{bracher2021evaluating}. Each representation may be more or less 
appropriate than the others for a given problem but knowing how to interpret, 
score and contruct ensemble forecasts for a selected representation is a must 
when multiple forecasts of the same event are involved.

@@

\section{Probability Distributions}

A probabilistic forecast model may be represented in a number of ways. A 
forecast should always come with a point estimate for a prediction and a 
characterization of the uncertainty associated with the point prediction.
Common representations which we review include parametric distributions,
discretized bin probabilities, samples and quantile or interval values.
In what follows, let $D$ be a distribution.

\subsection{Parametric distributions}
In a parametric distribution representation we let $D := D(\theta)$ 
where $\theta$ is vector of known or unkown parameters contained in a parameter 
space. We consider a parametric distribution any probability distribution with a 
fixed parameter set and a known probability density function (pdf) or 
probability mass function (pmf) for continuous and discrete distributions
repsectively. The pdf or pmf is represented as $p(y|\theta)$ where $\theta$ is 
a parameter, usually unknown but estimated using given data.

The value of $p(\cdot|\theta)$ evaluated at $y$ is defined as 
$p(y|\theta) = P(D = y)$ or the probability that the random variable $D$ takes
on $y$. In the continuous case $P(D = y) = 0$ for all $y$, but the probability 
that $D$ falls within an interval $(a,b)$ is calculated as

$$P(a < y < b) = \int_a^b p(y|\theta) dy$$

(??Note: I'm trying to decide how detailed I should be here. Have I already said
more than is necessary? Should I define the CDF and inverse CDF functions?)

In forecast modeling with a parametric distribution, data is used to obtain a 
likelihood function $L(\theta|y)$ and the unknown parameter $\theta$ is 
estimated as $\hat{\theta}$. (more/less detail ??) The mean or the median is
then used as a point estimate of the forecast and estimated probabilities for 
all other possible values may be calculated. For the most commonly used families
of distributions (Normal, Gamma, Poisson etc.) calculating point estimates and 
probabilities is easy due to the availability of software.

@@

Scoring rules are used to assign a numeric score to a probability forecast. The
score is a measure on the accuracy of the forecast and where multiple forecasts
exist may provide a rank for each relative to the others. If a scoring rule is 
proper, then the highest possible reward is obtained by reporting the true 
distribution. The rule is strictly proper if that value is unique.(define??) 
Under proper
scoring rules, a forecaster has no incentive to be dishonest in their 
submission \cite{gneiting2007strictly}. This makes proper scoring rules ideal
for grading forecasts.

Commonly used proper scoring rules include the Logarithmic score (LogS), 
continuous rank probability score (CRPS) \cite{hersbach2000decomposition}
\cite{alves2013ncep} and the interval/Brier 
score \cite{gneiting2007strictly} among 
others. See also \cite{gneiting2014probabilistic}
section 3 for on proper scoring functions. Unless otherwise noted, the following
definitions/reviews can be found in the review by Krueger.

For a forecast with pdf/pmf $p_m(y)$, the Logarithmic score evaluates the 
probability of the observed value $y^*$. It is defined as

\begin{equation}
  LS(p_m,y*) = -log\;p_m(y^*)
\end{equation}

This scoring method is appropriate for scoring density forecasts as well as 
descretized bins. The smaller the score, the better the forecast.
Because the probability evaluation is only at the observed 
point \cite{reich2019accuracy} used a modified Logarithmic score 
known as the multibin logarithmic score (MBlogS) for scoring
forecasts. This allowed for a range of values to be considered "correct" or 
accurate. MGlogS is defined as

@@

\subsection{Ensemble}
A multi-model ensemble is a statistical model made by combining information from
2 or more individual statistical models. Private and public decisions are 
regularly made after combining information from multiple sources. For any given
situation, information from one source may shed light on a subject which other
sources fail to capture. Likewise one statistical model may provide perspective
that another model does not, so that when they are combined in an ensemble the 
resulting model is superior.

As probabilistic forecasting becomes more commonplace, so too does ensemble 
modeling. Multi-model ensembles have been used extensively in weather and
climate modeling see \cite{baran2018combining}, 
and they have been used increasingly in modeling infectious disease outbreaks
see for example \cite{yamana2016superensemble}. 
Multi-model ensembles allow for an incorporation of multiple signals -
often from differing data sources- and for individual model biases being canceled
out or reduced by biases in others \cite{reich2019accuracy}. (See specific citations in this paper 12-15??)
In several disease outbreak studies, multi-model ensemble forecasts have been 
shown to outperform individual model forecasts \cite{cramer2021evaluation} (see
10, 14-25 in this paper).

@@

\subsection{Storage}
For a forecast hub collecting many predictions, computer storage is something
that needs to be addressed. For a project involving many researchers, the 
number of forecast predictions can add up. For example, the repository for the
COVID-19 Forecast Hub predictions contained 85.4 million predictions as of 
February 5, 2022! (cite zoltr??)
When determining the goals of a forecast project, there should be consideration 
of the storage required for different representations.

>>>>

\usepackage{framed}
\usepackage{changepage}
\usepackage{amsfonts}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

@@

A probabilistic forecast is a forecast to which probabilities are assigned to 
various possible outcomes. There are a number of ways the probabilities or 
uncertainty may be represented. A common representation is either a continuous 
or
discrete parametric distribution function (a pdf or pmf). Much of the literature 
on calibration, sharpness and scoring of a forecast pertains to parametric 
distribution forecasts (see for example 
\cite{gneiting2007probabilistic},
\cite{gneiting2013combining} \cite{baran2018combining}).
Other common representations include samples \cite{krueger2016probabilistic}, 
discretized bins 
and quantile or interval type forecasts \cite{taylor2021evaluating} 
\cite{bracher2021evaluating}. Each representation may be more or less 
appropriate than the others for a given problem but knowing how to interpret, 
score and contruct ensemble forecasts for a selected representation is a must 
when multiple forecasts of the same event are involved.

@@

\section{Probabilistic Forecast Representations}

Before introducing discrete mixture distributions as a candidate for a
probabilistic forecast, we review representations already commonplace in 
forecasting. In a collaborative setting, certain aspects of each representation
should be considered. With each representation presented, 
commmon application of 
scoring, data storage and ensemble construction will be considered for each type
as well as other notable properties.

\subsection{Considerations...}
\subsubsection{Scoring}
Scoring rules are used to evaluate numerically a probability forecast. The
score is a measure on the accuracy of the forecast and where multiple forecasts
exist may provide a rank for each relative to the others. If a scoring rule is 
proper, then the highest possible reward is obtained by reporting the true 
distribution. The rule is strictly proper if that value is unique. 
Under proper
scoring rules, a forecaster has no incentive to be dishonest in their 
submission \cite{gneiting2007strictly}. This makes proper scoring rules ideal
for grading forecasts. We will limit our review of scoring methods to rules
which are proper.

\subsubsection{Storage}
For a forecast hub collecting many predictions, computer storage is something
that needs to be addressed. For a project involving many researchers, the 
number of forecast predictions can add up. For example, the repository for the
COVID-19 Forecast Hub predictions contained 85.4 million predictions as of 
February 5, 2022! (cite zoltar??)
When determining the goals of a forecast project, there should be consideration 
of the storage required for different representations.

\subsubsection{Ensemble Modeling}
A multi-model ensemble is a statistical model made by combining information from
2 or more individual statistical models. Private and public decisions are 
regularly made after combining information from multiple sources. For any given
situation, information from one source may shed light on a subject which other
sources fail to capture. Likewise one statistical model may provide perspective
that another model does not, so that when they are combined in an ensemble the 
resulting model is superior.

As probabilistic forecasting becomes more commonplace, so too does ensemble 
modeling. Multi-model ensembles have been used extensively in weather and
climate modeling see \cite{baran2018combining}, 
and they have been used increasingly in modeling infectious disease outbreaks
see for example \cite{yamana2016superensemble}. 
Multi-model ensembles allow for an incorporation of multiple signals -
often from differing data sources- and for individual model biases being canceled
out or reduced by biases in others (\cite{reich2019accuracy} see references
therein). 
In several disease outbreak studies, multi-model ensemble forecasts have been 
shown to outperform individual model forecasts (\cite{cramer2021evaluation} see
references therein).

\subsection{Representations}
\subsubsection{Parametric distributions}
A parametric distribution is a discrete or continuous probability distribution 
described by a known function $p(x) := p(x|\theta)$ -pmf in the discrete case or 
pdf in the continuous case. $\theta$ is a vector of known or unkown parameters 
contained in a parameter space.

The value of $p(\cdot)$ evaluated at $x$ is defined as 
$p(x) = P(X = x)$ or the probability that the random variable $X$ takes
on $x$ in the space of the random variable. In the continuous case 
$P(D = x) = 0$ for all $x$, but the probability 
that $X$ falls within an interval $(a,b)$ is calculated as

\begin{equation}
  P(a < X < b) = \int_a^b p(x) dx
\end{equation}

Other functions classified by a parameteric distribution include the cumulative
distribution function (CDF) and the inverse CDF or quantile function. The CDF 
in the continuous case is defined as

\begin{equation}
  F_X(x) = P(X \leq b) = \int_{-\infty}^x p(t) dt
\end{equation}
or in the discrete case

\begin{equation}
  F_X(x) = P(X \leq b) = \sum_{k=1}^n p(x_k) dt
\end{equation}
where $x_n$ is the largest value of X less than or equal to $x$.
The quantile function is defined as
\begin{equation}
  Q(p) = \inf \{ y \in \mathbb{R} : p \leq F_X(x) \}
\end{equation}
returning a quantile value where $p$ is a given probability $0\leq p \leq 1$.

For a forecast represented as a parametric function with pmf/pdf $p_m(x)$, 
the accuracy of the forecast may be measured as how likely realized value $x^*$
is to occur. Commonly used proper scoring rules for parametric distributions
include the Logarithmic score (LogS), 
continuous rank probability score (CRPS) \cite{hersbach2000decomposition}
\cite{alves2013ncep} and the interval/Brier 
score \cite{gneiting2007strictly} among 
others. See also \cite{gneiting2014probabilistic}
section 3 for on proper scoring functions. Unless otherwise noted, the following
definitions/reviews can be found in the review by Krueger.

For a forecast with pdf/pmf $p_m(x)$, the Logarithmic score evaluates the 
probability of the observed value $x^*$. It is defined as

\begin{equation}
  LS(p_m,x*) = -log\;p_m(x^*)
\end{equation}

@@

Because the probability evaluation is only at the observed 
point \cite{reich2019accuracy} used a modified Logarithmic score 
known as the multibin logarithmic score (MBlogS) for scoring
forecasts. This allowed for a range of values to be considered "correct" or 
accurate. MGlogS is defined as

@@

\subsection{Ensemble}

@@

\subsection{Storage}
